Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-09-04 paper/paper.tex
minor typos

Having constrained only 3 parameters one might wonder why the other 11
parameters do not seem to matter.
In our case this can be explained by the large value of $P_{\rm cl}$
favored by \tol's observations. 
A large proability of having \lya\ photons emitted in the clumps
makes radiative transfer effects, and therefore other parameters such
as the clump column density, less relevant for the emergent line
profile.

@@

{\bf Which model could be closer to the actual kinematic conditions in \tol?  
Integral Field Unit (IFU) observations of other CDGs seem to
favor the multiphase model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
\citep{2003SPIE.4841.1670L}.
The spatial smapling was $0.67^{\prime\prime}$ and covered about
$30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
They observed nine BCGs to produce two-dimensional maps of the
continuum and promiment emission lines to finally compute velocitity
field maps using the H$\alpha$ emission line. 
They find velocity fields ranging from simple rotation patterns 
(with amplitudes of $10-120$ \kms) to highly irregular. 
The typical velocity dispersion values are in the range $10-50$ \kms
with the exception of one galaxy that shows a dispersion of $130$
\kms. }

>>>>

Having constrained only 3 parameters one might wonder why the other 11
parameters do not seem to matter.
In our case this can be explained by the large value of $P_{\rm cl}$
favored by \tol's observations. 
A large probability of having \lya\ photons emitted in the clumps
makes radiative transfer effects, and therefore other parameters such
as the clump column density, less relevant for the emergent line
profile.

@@

{\bf Which model could be closer to the actual kinematic conditions in \tol?  
Integral Field Unit (IFU) observations of other CDGs seem to
favor the multiphase model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
\citep{2003SPIE.4841.1670L}.
The spatial sampling was $0.67^{\prime\prime}$ and covered about
$30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
They observed nine BCGs to produce two-dimensional maps of the
continuum and prominent emission lines to finally compute velocity
field maps using the H$\alpha$ emission line. 
They find velocity fields ranging from simple rotation patterns 
(with amplitudes of $10-120$ \kms) to highly irregular. 
The typical velocity dispersion values are in the range $10-50$ \kms
with the exception of one galaxy that shows a dispersion of $130$
\kms. }
